%-------------------------
% Resume in Latex
% Author  : Mohit Sharma
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage{xcolor}
\usepackage{siunitx}
\input{glyphtounicode}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-0.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

% Sections formatting
\titleformat{\section}{
\vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{orange} \titlerule \vspace{-5pt}]

%-------------------------
% Custom commands
\newcommand{\resumeItem}[2]{
\item\small{
\textbf{#1}{: #2 \vspace{-2pt}}
}
}

\newcommand{\resumePubItem}[3]{
\item\small{
\textbf{#1 \null\hfill{#2}}{#3} \vspace{-2pt}
}
}

\newcommand{\resumeSubheading}[4]{
\vspace{-1pt}\item
\begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
    \textbf{#1}       & #2                 \\
    \textit{\small#3} & \textit{\small #4} \\
\end{tabular*}\vspace{-3pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \vspace{3pt}
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}\vspace{-4pt}}

\newcommand{\resumePublicationItem}[3]{\resumePubItem{#1}{#2}\newline{#3}\vspace{-4pt}}

\renewcommand{\labelitemii}{$\circ$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

\newcommand{\resumeTilde}{\raise.17ex\hbox{$\scriptstyle\sim$}}
%-------------------------------------------
%%%%%%  CV STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING-----------------
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
\textbf{\href{https://sharmamohit.com/} {\color[HTML]{DF691A} Mohit Sharma}} & \color[HTML]{DF691A} Email : \href{mailto:mohitsharma44@gmail.com}{mohitsharma44@gmail.com}\\
\href{https://sharmamohit.com/}{https://www.sharmamohit.com}  & LinkedIn : \href{https://linkedin.com/in/mohitsharma44/}{linkedin.com/in/mohitsharma44}\\
\end{tabular*}


%-----------SUMMARY-------------------
\section{\color[HTML]{DF691A} Summary}
DevOps Engineer with 10+ years of experience automating and scaling mission-critical systems. Proven expertise in Kubernetes, AWS, and Linux, with a strong focus on reducing operational complexity, enhancing developer experience, and fostering cross-functional collaboration. A track record of driving infrastructure automation, mentoring teams, and implementing best practices to deliver resilient, highly available systems.

%-----------EXPERIENCE-----------------
\section{\color[HTML]{DF691A} Experience}
\resumeSubHeadingListStart

\resumeSubheading
{Angi Inc}{Remote}
{Senior Infrastructure Engineer}{Sept 2023 - Present}
\resumeItemListStart
\resumeItem{Angi One}{}
\newline
{\textbf{-} Collaborated with cross-functional teams to build key components of the Angi One platform using Kubernetes controllers, Flux, and ArgoCD, enabling single-manifest deployments for applications and cloud services, reducing developer overhead and cutting production time by 50\%.}
\newline
{\textbf{-} Led efforts to automate documentation workflows based on CRDs, ensuring up-to-date documentation with every release, reducing manual effort and support inquiries.}
\newline
{\textbf{-} Partnering with development and observability teams to enhance and automate component generation in the Backstage catalog, streamlining the onboarding process and improving system visibility.}
\resumeItemListEnd

\resumeSubheading
{Workday}{Victoria, BC, Canada}
{Senior Software Development Engineer, DevOps}{May 2023 - Sept 2023.}
\resumeSubSubheading
{Software Development Engineer III, DevOps}{May 2021 - April 2023.}
\resumeSubSubheading
{Software Development Engineer II, DevOps}{May 2019 - April 2021.}
\resumeItemListStart
\resumeItem{Development and Operations}{}
\newline
{\textbf{-} Implemented policy-based infrastructure management using 
\href{https://www.openpolicyagent.org/}{OPA} and \href{https://www.runatlantis.io/}{Atlantis} 
improving developer experience while providing them more control over their resources and helping them shift 
security best practices to the left.}
\newline
{\textbf{-} Mentored developers and junior engineers as they grew into their role.}
\newline
{\textbf{-} Created an automated AWS deployment pipeline to deploy microservice application cross account and cross region
reducing operations toil by over 4 hours every week.}
\newline
{\textbf{-} Actively manage, improve, and monitor infrastructure resources in DC and on AWS including but not limited to
EC2, ECS, Route53, S3, RDS, Lambda, ES etc. using tools like ansible, terraform, wavefront, ELK stack and slackbot.}
\newline
{\textbf{-} Writing Jenkinsfiles and improving shared libraries for automated build and deployment of several applications and services using Jenkins.}
\newline
{\textbf{-} Migrating applications and services to an in-house flavor of Kubernetes platform.}
\resumeItem{Knowledge Share}{Spearheaded an initiative between operations and multiple dev teams to empower the developers with the knowledge
they would need to take ownership of their services.}
\resumeItem{Scrum Master}{Helped team self organize and self manage by incorporating servant leadership principles.}
\resumeItemListEnd

\resumeSubheading
{NYU CUSP}{Brooklyn, NY, USA}
{Associate Research Scientist}{May 2015 - May 2019}
\resumeSubSubheading
{Assistant Research Scientist}{June 2014 - May 2015.}
\resumeItemListStart
\resumeItem{Dockkeeper}
{Developed a scalable and secure container scheduling and monitoring tool that leverages the docker ecosystem and prometheus for provisioning services on physical hosts. This helped eliminate the VM license fees of over \$35,000 per year and optimizing the efficiency of hosts by over 55\%.}
\resumeItem{UOInfra}
{Architected the NYU/CUSP Urban Observatory's multi-site physical infrastructure consisting of multiple dense compute and storage nodes comprising of over half a petabyte of storage space, provisioned for multi-user mini-HPC environments, using Ansible and Packer.\\
Deployed a 27 screen vizwall using a cluster of networked raspberry Pi's enabling researchers to interpret their visualizable data, while keeping the whole price to 1/8 th of that of a commercial solution.}
\resumeItem{SONYC}
{Developed a secure machine critical IoT platform and implemented CI/CD framework for deploying and maintaining over 100 urban noise monitoring sensors in NYC. This project has won the \href{https://www.nsf.gov/awardsearch/showAward?AWD_ID=1544753}{\$ $4.6$ Million} CPS frontier award from NSF. }
\resumeItemListEnd
\resumeSubHeadingListEnd

%-----------EDUCATION-----------------
\section{\color[HTML]{DF691A} Education}
\resumeSubHeadingListStart
\resumeSubheading
{NYU Tandon School of Engineering}{Brooklyn, NY, USA}
{Master of Science in Telecommunication Networks}{Aug. 2012 -- May. 2014}

\textit{\small{Thesis - \href{https://sharmamohit.com/project/citysynth/}{CitySynth: Imaging with a Network of Devices}}}
\resumeSubHeadingListEnd


%-----------CERTIFICATIONS-----------
\section{\color[HTML]{DF691A} Certifications}
\resumeSubHeadingListStart
\resumeSubItem{CKA Certified Kubernetes Administrator} \null\hfill \textit{\small{}}
\resumeSubHeadingListEnd

%-----------PROJECTS-----------------
\section{\color[HTML]{DF691A} Projects}
\resumeSubHeadingListStart
% \resumeSubItem{CUIC}
% {Open source python library for interfacing with GigE vision broadband, thermographic and hyperspectral cameras using advanced message queuing protocol to acquire images and perform pre-processing on-the-fly.}
\resumeSubItem{AdguardController}
{Developed a Kubernetes controller to automate DNS record management, significantly improving deployment efficiency and reducing manual errors.}
\resumeSubItem{UCSLHUB}
{Developed a resilient and scalable back-end infrastructure using Kubernetes, jupyterhub and keycloak for hosting the CUSP's UCSL bootcamp \textbf{which is accessed by hundreds of students every year}.}
\resumeSubItem{MUON}
{Developed a research and analysis platform for scientists in the Multi-City Urban Observatory Network at the University of Delaware.}
\resumeSubItem{Homelab}
{Running a HCI homelab with ansible and terraform managed KVM nodes with Ceph running behind a Pfsense firewall that is used for testing and development including emulation of distributed datacenters.}
\resumeSubHeadingListEnd

\section{\color[HTML]{DF691A} Publications, Teaching Experience and more..}
\resumeSubHeadingListStart
\resumeItem{View it online}{\href{https://sharmamohit.com/work/}{https://sharmamohit.com/}}
\newline
\resumeSubHeadingListEnd

\end{document}
